### 2020-02-27 Article.tex
Auto stash before merge of "master" and "origin/master"

\begin{definition}
	Let $\Sigma$ be a set containing the empty label $\emptyset$. A rooted $\Sigma$-edge
	is a $\Sigma$-hypergraph $(e,\chi)$ where $e$ is an edge 
	(i.e., an hypergraph consisting of only one edge), $v\in V(e)$ is a vertex called the root 
	of $e$, and $\chi: V(e)\rightarrow \Sigma$ such that $\chi(u)=\emptyset$ if and only if 
	$u=v$.\par
	Given a rooted $\Sigma$-edge $(e,v,\chi)$, a set $V$ and a 
\end{definition}

\begin{definition}

>>>>

\begin{definition}
	Let $\Sigma$ be a set containing the empty label $\emptyset$. A rooted $\Sigma$-edge
	is a $\Sigma$-hypergraph $(e,\chi)$ where $e$ is an edge 
	(i.e., an hypergraph consisting of only one edge), and there is a unique vertex
	$v\in V(e)$ such that $\chi(v)=\emptyset$.
	Given a rooted $\Sigma$-edge $(e,v,\chi)$, a set $V$ and a 
	(i.e., an hypergraph consisting of only one edge), $v\in V(e)$ is a vertex called the root 
	of $e$, and $\chi: V(e)\rightarrow \Sigma$ such that $\chi(u)=\emptyset$ if and only if 
	$u=v$.\par
	Given a rooted $\Sigma$-edge $(e,\chi)$, a set of vertices $V$ and a vertex $v\in \N$
	we define the set $Copies((e,\chi),(V,v))$ as the set of copies 
	$(e^\prime, \chi^\prime) \in  Copies((e,\chi),V)$ such that $v$ is
	 the root of $(e^\prime,\chi^\prime)$.
\end{definition}

\begin{definition} 
	Let $V$ be a finite set of vertices
